Solution

Package used
```{r}
options(java.parameters = c("-XX:+UseConcMarkSweepGC", "-Xmx8192m"))
require(xlsx)
require(sqldf)
require(ggplot2)
require(mclust)
require(rpart)
require(rpart.plot)
```

data input
```{r}
sales <- read.xlsx("Sale_Data.xlsx", sheetName = "Sales_Record", encoding = "UTF-8")
product <- read.xlsx("Sale_Data.xlsx", sheetName = "Product_Information", encoding = "UTF-8")
```

Data Observation / Cleansing
```{r}
#prove there are 70680 sales records
nrow(sales) == 70680
#prove product name in both dataset are synchronized
length(setdiff(sales$商品, product$商品)) == 0
#prove product_price = actual paid

#list any uncleaned data for cleansing if necessary
sales$应付金额 <- as.numeric(sales$应付金额)
sales$实际金额 <- as.numeric(sales$实际金额)

df <- sales

df$equal <- abs(df$应付金额 - df$实际金额) < 1e-9

table(df$equal)

if (all(df$equal)) {
  print("PROVEN: product_price == actual_paid for all records")
} else {
  print(paste("Mismatches found:", sum(!df$equal)))
 
  df[!df$equal, c("product_price", "actual_paid")]
}
```

Merge Data
```{r}
merged_data <- merge(sales, product, by = "商品", all.x = TRUE)
merged_data$Month <- format(merged_data$支付时间, "%m")
merged_data$Date <- format(merged_data$支付时间, "%Y-%m-%d")
merged_data$Day <- format(merged_data$支付时间, "%d")
```

Mission 1.1 According to the merged dataset, suppose each location only have one vendor machine. Extract the Sales record from the merged dataset and store the data separately based on the Vendor machine location "A", "B", "C", "D", "E".
```{r}
sales_A <- subset(merged_data, 地点 == "A")
sales_B <- subset(merged_data, 地点 == "B")
sales_C <- subset(merged_data, 地点 == "C")
sales_D <- subset(merged_data, 地点 == "D")
sales_E <- subset(merged_data, 地点 == "E")
```

Mission 1.2 Calculate each vending machine’s sales revenue and number of orders for April 2017, and also compute the overall total sales revenue and total number of orders across all vending machines. Display the results in a table within the report.
```{r}
april_sales <- subset(merged_data, format(支付时间, "%Y-%m") == "2017-04")
mission1_2 <- sqldf("SELECT 地点 as Location, COUNT(订单号) as 'Sale Volume', SUM(实际金额) as Revenue FROM april_sales GROUP BY 地点")
print(mission1_2)

print(paste("Overall Orders:", nrow(april_sales), "Overall Revenue:", sum(april_sales$实际金额)))
```

Mission 1.3 Summaries the monthly average Revenue of each Vendor machine and also it is daily average Sale volume.
```{r}
monthly_revenue <- sqldf("SELECT 地点 as Location, Month, SUM(实际金额) as Revenue FROM merged_data GROUP BY 地点, Month")

daily_volume <- sqldf("SELECT 地点 as Location, Date, COUNT(订单号) as Volume FROM merged_data GROUP BY 地点, Date")
avg_daily_volume <- sqldf("SELECT Location, AVG(Volume) as Avg_Daily_Volume FROM daily_volume GROUP BY Location")
```

Mission2.1 visualise the top 5 sale product in June 2017 using bar chart
```{r}
june_sales <- subset(merged_data, Month == "06")
top5_products <- sqldf("SELECT 商品, COUNT(订单号) as Volume FROM june_sales GROUP BY 商品 ORDER BY Volume DESC LIMIT 5")

ggplot(top5_products, aes(x = reorder(商品, -Volume), y = Volume, fill = 商品)) +
  geom_bar(stat = "identity") + theme_minimal() +
  labs(title = "Best Five Sale Products in June 2017", x = "Product", y = "Sale Volume") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

Mission 2.2 visualise all vendor machine revenue trend in monthly basis and also its growth rate in bar chart.
```{r}
monthly_trend <- sqldf("SELECT 地点 as Location, Month, SUM(实际金额) as Monthly_Revenue FROM merged_data GROUP BY Location, Month")
monthly_trend <- monthly_trend[order(monthly_trend$Location, monthly_trend$Month), ]
monthly_trend$Growth_Rate <- ave(monthly_trend$Monthly_Revenue, monthly_trend$Location, 
                                 FUN = function(x) c(NA, diff(x) / x[-length(x)]))

ggplot(monthly_trend, aes(x = Month, y = Monthly_Revenue, group = Location, color = Location)) +
  geom_line() + geom_point() +
  labs(title = "Vendor Machine Revenue Trend in Monthly Basis", x = "Month", y = "Monthly Revenue")

ggplot(na.omit(monthly_trend), aes(x = Month, y = Growth_Rate, fill = Location)) +
  geom_bar(stat = "identity", position = "dodge") + facet_wrap(~ Location) +
  labs(title = "Growth Rate by Vendor Machine", x = "Month", y = "Growth Rate")
```

Mission2.3 plot margin revenue proportion for each vendor machine. Suppose the margin revenue rate of beverage and non-beverage is 25% and 20% respectively.
```{r}
merged_data$Margin <- ifelse(merged_data$大类 == "饮料", merged_data$实际金额 * 0.25, merged_data$实际金额 * 0.20)
margin_data <- sqldf("SELECT 地点, 大类, SUM(Margin) as Total_Margin FROM merged_data GROUP BY 地点, 大类")

ggplot(margin_data, aes(x = "", y = Total_Margin, fill = 大类)) +
  geom_bar(stat = "identity", width = 1, position = "fill") +  # Added position = "fill" here
  coord_polar("y", start = 0) +
  facet_wrap(~ 地点) + 
  theme_void() +
  labs(title = "Margin Revenue Proportion for Each Vendor Machine")
```

Mission 2.4 - plot the total revenue of each machines in April 2027 by bubble chart
```{r}
ggplot(mission1_2, aes(x = Location, y = Revenue, size = Revenue)) +
  geom_point(alpha = 0.7, color = "black") + scale_size(range = c(5, 15)) +
  labs(title = "Total Revenue of Each Machine in April 2017", x = "Location", y = "Total Revenue") + theme_minimal()
```

Mission 2.5 - plot the revenue of Vendor machine C in June, July, and August and summmarise the data by heatmap graph.
```{r}
c_summer <- subset(merged_data, 地点 == "C" & Month %in% c("06", "07", "08"))
c_heatmap <- sqldf("SELECT Month, Day, SUM(实际金额) as Daily_Revenue FROM c_summer GROUP BY Month, Day")

c_heatmap$Day <- factor(c_heatmap$Day, levels = sprintf("%02d", 1:31))

ggplot(c_heatmap, aes(x = Day, y = Month, fill = Daily_Revenue)) +
  geom_tile(color = "white") + 
  scale_fill_gradient(low = "lightblue", high = "darkblue", na.value = "white") +
  labs(title = "Revenue Heatmap of Machine C (Jun-Aug)", x = "Day", y = "Month", fill = "实际金额") + 
  theme_minimal()
```
Mission 3.1
Use any machine learning approach to auto labelling the salse status of each brevage products in each Vendor machine. There are three types of labels : unsaleable, normal, trending. In which, unsaleable means the salse status was uncertain, and normal means there is no observable sale pattern, treding mean the sale is good. 

```{r}
beverage_data <- subset(merged_data, 大类 == "饮料")
bev_status <- sqldf("SELECT 商品, 地点 as Location, COUNT(订单号) as SaleVolume FROM beverage_data GROUP BY 商品, 地点")

set.seed(123)
cluster_model <- Mclust(bev_status$SaleVolume, G = 3)
bev_status$Cluster <- cluster_model$classification

cluster_means <- aggregate(SaleVolume ~ Cluster, data = bev_status, mean)
cluster_means <- cluster_means[order(cluster_means$SaleVolume), ] 

labels_mapping <- setNames(c("unsalable", "normal", "trending"), cluster_means$Cluster)

bev_status$Label <- labels_mapping[as.character(bev_status$Cluster)]

head(bev_status)
```

Mission 3.2  Use any machine learning approach to classify the sale segnments of different types of product category by the relationship of the Category total Revenue.
```{r}
category_sales <- sqldf("SELECT 二级类 as Category, SUM(实际金额) as TotalRevenue FROM merged_data GROUP BY Category")

quants <- quantile(category_sales$TotalRevenue, probs = c(0.33, 0.66))
category_sales$Segment <- ifelse(category_sales$TotalRevenue < quants[1], "Low",
                                 ifelse(category_sales$TotalRevenue < quants[2], "Medium", "High")
                                 )

tree_model <- rpart(Segment ~ TotalRevenue, data = category_sales, method = "class")
prp(tree_model, main="Product Category Sales Segments", extra=104, box.palette="RdYlGn")
```
